 \documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
 \usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
 \geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
 %\geometry{landscape}                		% Activate for for rotated page geometry
 %\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
 \usepackage{graphicx}				% Use pdf, png, jpg, or eps with pdflatex; use eps in DVI mode
 								% TeX will automatically convert eps --> pdf in pdflatex		
 \usepackage{amssymb}
 \usepackage{pdflscape}
\usepackage{fullpage}
 \title{Notes on ``Creativity'' by Mihaly Csikszentmihalyi}
 \author{J. Jason Bell}
 \date{}							% Activate to display a given date or no date

 \begin{document}
 \maketitle
 %\section{}
 %\subsection{}

\begin{enumerate}
\item Major creativity is minor creativity which is attached to a domain and gets recognized by the field in that domain.  In marketing, the domain is a product category, and the field is the consumer, probably.
\item Criteria for evaluating a \textit{set} of ideas:
	\begin{itemize}
	\item Fluency: number of ideas
	\item Flexibility: variety of ideas.  Space spanned by idea vectors?  Variance between ideas?
	\item Novelty: Originality
	\end{itemize}
	This seems like an incomplete list.  In our case, we also need feasibility and market demand.  What dataset would you need to predict feasibility and market demand?  For feasibility you'd need time from conception to market.  Market demand you'd need sales in the first year or something.
\item The most creative individuals are good at simulating the reaction of the field to their idea, so they are more efficient in throwing out ideas, and then they can produce more.  Since creativity is mostly a numbers game, efficiency is everything.  The sooner you can correctly throw out a bad idea, the better, but throwing out a good idea accidentally is worse than keeping a bad one.  Bayesian decision theory.  
	
\end{enumerate}

\end{document}  